<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{vcr introduction}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE
)
```

vr introduction
===============

Record 'HTTP' Calls to Disk

Right now `vcr` is not yet using previously cached requests, but will soon.

## installation

Development version from GitHub

```{r eval=FALSE}
devtools::install_github("ropenscilabs/vcr")
```

Load `vcr`

```{r}
library("vcr")
```

## examples

list cassettes

```{r}
cassettes()
```

list the current cassette

```{r}
cassette_current()
```

coerce various things to cassette objects

```{r eval=FALSE}
as.cassette("helloworld")
as.cassette(cassettes()[1])
as.cassette(as.cassettepath("~/vcr/vcr_cassettes/cheese.yml"))
```

list the path to where cassettes are stored

```{r}
cassette_path()
```

insert a cassette

```{r}
insert_cassette(name = "fartloud")
```

use a cassette (if cassette not found, we'll create the cassette)

```{r}
use_cassette("helloworld", GET("http://localhost:9200"))
```

You can also pass a code block, instead of an inline call

```{r}
insert_cassette("foobar")
call_block("foobar", {
  url <- "http://localhost:9200"
  GET(url)
})
```
