---
title: "Why and how edit your vcr cassettes?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{5. cassette manual editing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vcr)
```

## Why edit cassettes?

By design vcr is very good at recording HTTP interactions that actually took place.
Now sometimes when testing/demo-ing your package you will want to use _fake_ HTTP interactions.
For instance:

* What happens if the web API returns a 503 code? Is there an informative error?
* What happens if it returns a 503 and then a 200 code? Does the retry work?
* What if the API returns too much data for even simple queries and you want to make your cassettes smaller?

In all these cases, you can edit your cassettes as long as you are aware of the risks!

## Risks related to cassette editing

* If you use a vcr cassette where you replace a 200 code with a 503 code, and vcr is turned off, 
the test will fail because the API will probably not return an error.
* If you edit cassettes by hand you can't re-record them easily, you'd need to re-record them then re-apply your edits.

Therefore you'll need to develop a good workflow.

## Example 1: test using an edited cassette with a 503

First, write your test e.g.

```r
vcr::use_cassette("api-error", {
  testhat("Errors are handled well", {
    vcr::skip_if_vcr_off()
    expect_error(call_my_api()), "error message")
  })
})

```

Then run your tests a first time.

1. It will fail
2. It will have created a cassette under `tests/fixtures/api-error.yml` that looks 
something like

```yaml
http_interactions:
- request:
    method: get
    uri: https://eu.httpbin.org/get
    body:
      encoding: ''
      string: ''
    headers:
      User-Agent: libcurl/7.54.0 r-curl/3.2 crul/0.5.2
  response:
    status:
      status_code: '200'
      message: OK
      explanation: Request fulfilled, document follows
    headers:
      status: HTTP/1.1 200 OK
      connection: keep-alive
    body:
      encoding: UTF-8
      string: "{\n  \"args\": {}, \n  \"headers\": {\n    \"Accept\": \"application/json,
        text/xml, application/xml, */*\", \n    \"Accept-Encoding\": \"gzip, deflate\",
        \n    \"Connection\": \"close\", \n    \"Host\": \"httpbin.org\", \n    \"User-Agent\":
        \"libcurl/7.54.0 r-curl/3.2 crul/0.5.2\"\n  }, \n  \"origin\": \"111.222.333.444\",
        \n  \"url\": \"https://eu.httpbin.org/get\"\n}\n"
  recorded_at: 2018-04-03 22:55:02 GMT
  recorded_with: vcr/0.1.0, webmockr/0.2.4, crul/0.5.2
```

You can edit to (new status code)

```yaml
http_interactions:
- request:
    method: get
    uri: https://eu.httpbin.org/get
    body:
      encoding: ''
      string: ''
    headers:
      User-Agent: libcurl/7.54.0 r-curl/3.2 crul/0.5.2
  response:
    status:
      status_code: '503'
```

And run your test again, it should pass!
Note the use of `vcr::skip_if_vcr_off()`: if vcr is turned off, there is a real 
API request and most probably this request won't get a 503 as a status code.

### The same thing with webmockr

The advantage of the approach involving editing cassettes is that you only learn
 one thing, which is vcr.
Now, by using the webmockr directly in your tests, you can also test for the 
behavior of your package in case of errors.
Below we assume `api_url()` returns the URL `call_my_api()` calls.

```r
testhat("Errors are handled well", {
  webmockr::enable()
  stub <- webmockr::stub_request("get", api_url())
  webmockr::to_return(stub, status = 503)
  expect_error(call_my_api()), "error message")
  webmockr::disable()

})

```

A big pro of this approach is that it works even when vcr is turned off.
A con is that it's quite different from the vcr syntax.

## Example 1: test using an edited cassette with a 503 then a 200

## Conclusion

In this vignette we saw why and how to edit your vcr cassettes.
We also presented approaches that use webmockr instead of vcr for mocking API responses.
We mentioned editing cassettes by hand but you could also write a script using the `yaml` 
or `jsonlite` package to edit your YAML/JSON cassettes programmatically.
