---
title: "Configure vcr"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output: html_vignette
vignette: >
  %\VignetteIndexEntry{2. vcr configuration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE,
	eval = FALSE
)
```

vcr configuration
=================

`vcr` configuration

```{r}
library("vcr")
```


```{r}
library("vcr")
```

You can also get the default configuration variables via `vcr_config_defaults()`

```{r}
vcr_config_defaults()
```

These defaults are set when you load `vcr` - you can override any of them as described below.

## Set configuration variables

Use `vcr_configure()` to set configuration variables.

For example, set a single variable:

```{r}
vcr_configure(
  dir = "foobar/vcr_cassettes"
)
```

Or many at once:

```{r}
vcr_configure(
  dir = "foobar/vcr_cassettes",
  record = "all"
)
```

## Re-set to defaults

```{r}
vcr_configure_reset()
```

## Details on some of the config options

### dir

Directory where cassettes are stored

```{r}
vcr_configure(dir = "new/path")
```

### record

The record mode

One of: 'all', 'none', 'new_episodes', 'once'. See `?recording` for info on the options

```{r}
vcr_configure(record = "new_episodes")
```

### match_requests_on

Customize how `vcr` matches requests

```{r}
vcr_configure(match_requests_on = c('query', 'headers'))
```

### allow_unused_http_interactions

Allow HTTP connections when no cassette

Default is `TRUE`, and thus does not error when http interactions are unused. You
can set to `FALSE` in which case vcr errors when a cassette is ejected and
not all http interactions have been used.

```{r}
vcr_configure(allow_unused_http_interactions = FALSE)
```

### serialize_with

Which serializer to use: "yaml" or "json". Note that you can have
multiple cassettes with the same name as long as they use different
serializers; so if you only want one cassette for a given cassette name,
make sure to not switch serializers, or clean up files you no longer need.

```{r}
vcr_configure(serialize_with = "yaml")
```

### ignoring some requests

**ignore_hosts**

Specify particular hosts to ignore. By ignore, we mean that
real HTTP requests to the ignored host will be allowed to occur, while
all others will not.

```{r}
vcr_configure(ignore_hosts = "google.com")
```

**ignore_localhost**

Ignore all localhost requests

```{r}
vcr_configure(ignore_localhost = TRUE)
```

**ignore_request**

THIS DOESN'T WORK YET

**How to ignore requests**

For ignoring requests, you can for example, have real http requests go through (ignored by `vcr`) while other requests are handled by `vcr`. For example, let's say you want requests to `google.com` to be ignored:

```{r eval=FALSE}
vcr_configure(ignore_hosts = "google.com")
use_cassette("foo_bar", {
  crul::HttpClient$new("https://httpbin.org/get")$get()
  crul::HttpClient$new("https://google.com")$get()
})
```

The request to httpbin.org will be handled by `vcr`, a cassette created for the request/response to that url, while the google.com request will be ignored and not cached at all.

Note: ignoring requests only works for the `crul` package for now; it should work for `httr` and `httr2` in a later `vcr` version.

### preserve_exact_body_bytes

Some HTTP servers are not well-behaved and respond with invalid data. Set
`preserve_exact_body_bytes` to `TRUE` to base64 encode the result body in
order to preserve the bytes exactly as-is. `vcr` does not do this by
default, since base64-encoding the string removes the human readability
of the cassette.

```{r}
vcr_configure(preserve_exact_body_bytes = TRUE)
```
