---
title: "vcr configuration"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{2. vcr configuration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE
)
```

vr configuration
================

`vcr` configuration

```{r}
library("vcr")
```

## Get configuration

Use `vcr_configuration()` to get the current configuration

```{r}
vcr_configuration()
```

You can get the default configuration variables via `vcr_config_defaults()`

```{r}
vcr_config_defaults()
```

These defaults are set when you load `vcr` - you can override any of them as described below.

## Set configuration variables

Use `vcr_configure()` to set configuration variables.

For example, set a single variable:

```{r}
vcr_configure(
  dir = "foobar/vcr_cassettes"
)
```

Or many at once:

```{r}
vcr_configure(
  dir = "foobar/vcr_cassettes",
  record = "all"
)
```

## Re-set to defaults

```{r}
vcr_configure_reset()
```

## Individual config options

### dir - directory of where cassettes are stored

```{r}
vcr_configure(dir = "new/path")
```

### record - record mode

One of: 'all', 'none', 'new_episodes', 'once'. See `?recording` for info on the options

```{r}
vcr_configure(record = "new_episodes")
```

### match_requests_on - customize how vcr matches requests

```{r}
vcr_configure(match_requests_on = c('query', 'headers'))
```

### allow_unused_http_interactions - Allow HTTP connections when no cassette

Default is `TRUE`, and thus does not error when http interactions are unused. You 
can set to `FALSE` in which case vcr errors when a cassette is ejected and 
not all http interactions have been used.

```{r}
vcr_configure(allow_unused_http_interactions = FALSE)
```

### serialize_with - which serializer to use

Right now only option is "yaml"

```{r}
vcr_configure(serialize_with = "yaml")
```

### persist_with - which persister to use

Right now only option is "FileSystem"

```{r}
vcr_configure(persist_with = "FileSystem")
```

### ignore_hosts - specify particular hosts to ignore

```{r}
vcr_configure(ignore_hosts = "google.com")
```

### ignore_localhost - ignore all localhost flavors

```{r}
vcr_configure(ignore_localhost = TRUE)
```

### ignore_request - ignore any request for which function is true

```{r}
vcr_configure(ignore_request = function(x) x == 5)
```

### uri_parser - which uri parser to use

By default we use `httr::parse_url`, but you can use a different one. Remember 
to pass in the function quoted, and namespaced.

```{r}
vcr_configure(uri_parser = "urltools::url_parse")
```

### preserve_exact_body_bytes

Some HTTP servers are not well-behaved and respond with invalid data. Set 
`preserve_exact_body_bytes` to `TRUE` to base64 encode the result body in 
order to preserve the bytes exactly as-is. `vcr` does not do this by
default, since base64-encoding the string removes the human readibility 
of the cassette.

```{r}
vcr_configure(preserve_exact_body_bytes = TRUE)
```
