---
title: "vcr introduction"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{1. vcr introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE,
  eval = FALSE
)
```

vcr introduction
================

`vcr` is an R port of the Ruby gem [VCR](https://github.com/vcr/vcr) (i.e., a translation, there's no Ruby here :))

`vcr` helps you stub HTTP requests so you don't have to repeat HTTP requests.

The main use case is for unit tests, but you can use it outside of the unit test use case.

`vcr` works with the `crul` and `httr` HTTP request packages; we're working on support for `curl`.

Check out the [http testing book](https://books.ropensci.org/http-testing/) for a lot more documentation on `vcr`, `webmockr`, and `crul`

## Installation

CRAN

```{r eval=FALSE}
install.packages("vcr")
```

Development version

```{r eval=FALSE}
remotes::install_github("ropensci/vcr")
```

```{r}
library("vcr")
```

## Getting Started

### `use_vcr`

Setting up your package to use `vcr` for testing is easy with the built in setup function.

```r
vcr::use_vcr()
```

This will:

* put `vcr` into the `DESCRIPTION`
* check that `testthat` is setup
* setup `testthat` if not
* set the recorded cassettes to be saved in and sourced from `tests/fixtures`
* setup a config file for `vcr`
* add an example test file for `vcr`
* make a `.gitattributes` file with settings for `vcr` 
* make a `./tests/testthat/helper-vcr.R` file

### Protecting secrets

Secrets often turn up in API work. A common example is an api-key. VCR _records_ the full response from the API, which will include things like api-keys if they are present. You need to be able to protect these pieces of information from things like version control, but still have them be accessible to the tests so that they can run as expected. The `vcr_configure` function has the `filter_sensitive_data` argument function for just this situation. The `filter_sensitive_data` argument takes a named list where the _name_ of the list is the string that will be used in the recorded cassettes _instead of_ the secret, which is the list _item_. `vcr` will manage the replacement of that for you, so all you need to do is to edit your `helper-vcr.R` file like this:

```r
library("vcr")
invisible(vcr::vcr_configure(
  filter_sensitive_data = list("<<<my_api_key>>>" = Sys.getenv('APIKEY'),  # add this
  dir = "../fixtures"
))
vcr::check_cassette_names()
```

It is normal to keep your secrets as environmental variables local to your system. The addition of the line above will instruct `vcr` to replace any string in cassettes it records that are equivalent to your string which is stored as the `APIKEY` environmental variable with the masking string `<<<my_api_key>>>`. In practice, you might get a `YAML` that looks a little like this:

```yaml
http_interactions:
- request:
    method: post
    ...
    headers:
      Accept: application/json, text/xml, application/xml, */*
      Content-Type: application/json
      api-key: <<<my_api_key>>>
    ...
```
Here, my `APIKEY` environmental variable would have been stored as the `api-key` value, but `vcr` has realised this and recorded the string `<<<my_api_key>>>` instead.

When `vcr` then checks a test against this _local_ version of the response, it will then compare the `APIKEY` it _receives_ in the test against the one it _sources_ from the one sourced in the `vcr_configure`, which in this case comes from the local environment. Therefore, if you have to change the `APIKEY` in the future, the test will _still_ work as long as the local `APIKEY` environmental is up to date.

#### Using an `.Renviron`

A simple way to manage local environmental variables is to use an `.Renviron` file. Your `.Renviron` file might look like this:

```sh
APIKEY="mytotallysecretkey"
```

You can have this set at a project or user level, and `usethis` has the `usethis::edit_r_environ()` function to help edit the file.

## Basic usage

```{r echo=FALSE}
suppressPackageStartupMessages(require(vcr, quietly = TRUE))
unlink(file.path(cassette_path(), "helloworld.yml"))
```

```{r}
library(vcr)
library(crul)

cli <- crul::HttpClient$new(url = "https://eu.httpbin.org")
system.time(
  use_cassette(name = "helloworld", {
    cli$get("get")
  })
)
```

The request gets recorded, and all subsequent requests of the same form 
used the cached HTTP response, and so are much faster

```{r}
system.time(
  use_cassette(name = "helloworld", {
    cli$get("get")
  })
)
```

```{r echo=FALSE}
unlink(file.path(cassette_path(), "helloworld.yml"))
```

Importantly, your unit test deals with the same inputs and the same outputs - 
but behind the scenes you use a cached HTTP response - thus, your tests run faster.

The cached response looks something like (condensed for brevity):

```yaml
http_interactions:
- request:
    method: get
    uri: https://eu.httpbin.org/get
    body:
      encoding: ''
      string: ''
    headers:
      User-Agent: libcurl/7.54.0 r-curl/3.2 crul/0.5.2
  response:
    status:
      status_code: '200'
      message: OK
      explanation: Request fulfilled, document follows
    headers:
      status: HTTP/1.1 200 OK
      connection: keep-alive
    body:
      encoding: UTF-8
      string: "{\n  \"args\": {}, \n  \"headers\": {\n    \"Accept\": \"application/json,
        text/xml, application/xml, */*\", \n    \"Accept-Encoding\": \"gzip, deflate\",
        \n    \"Connection\": \"close\", \n    \"Host\": \"httpbin.org\", \n    \"User-Agent\":
        \"libcurl/7.54.0 r-curl/3.2 crul/0.5.2\"\n  }, \n  \"origin\": \"136.152.208.176\",
        \n  \"url\": \"https://httpbin.org/get\"\n}\n"
  recorded_at: 2018-04-03 22:55:02 GMT
  recorded_with: vcr/0.0.7.9324
```

All components of both the request and response are preserved, so that the HTTP 
client (in this case `crul`) can reconstruct its own response just as it would 
if it wasn't using `vcr`.
