---
title: "vcr introduction"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{1. vcr introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE,
  eval = FALSE
)
```

vcr introduction
================

`vcr` is an R port of the Ruby gem [VCR](https://github.com/vcr/vcr) (i.e., a translation, there's no Ruby here :))

`vcr` helps you stub HTTP requests so you don't have to repeat HTTP requests.

The main use case is for unit tests, but you can use it outside of the unit test use case.

`vcr` works with the `crul` and `httr` HTTP request packages; we're working on support for `curl`.

Check out the [http testing book](https://ropensci.github.io/http-testing-book/) for a lot more documentation on `vcr`, `webmockr`, and `crul`

## Installation

CRAN

```{r eval=FALSE}
install.packages("vcr")
```

Development version

```{r eval=FALSE}
remotes::install_github("ropensci/vcr")
```

```{r}
library("vcr")
```

## Basic usage

```{r echo=FALSE}
suppressPackageStartupMessages(require(vcr, quietly = TRUE))
unlink(file.path(cassette_path(), "helloworld.yml"))
```

```{r}
library(vcr)
library(crul)

cli <- crul::HttpClient$new(url = "https://eu.httpbin.org")
system.time(
  use_cassette(name = "helloworld", {
    cli$get("get")
  })
)
```

The request gets recorded, and all subsequent requests of the same form 
used the cached HTTP response, and so are much faster

```{r}
system.time(
  use_cassette(name = "helloworld", {
    cli$get("get")
  })
)
```

```{r echo=FALSE}
unlink(file.path(cassette_path(), "helloworld.yml"))
```

Importantly, your unit test deals with the same inputs and the same outputs - 
but behind the scenes you use a cached HTTP response - thus, your tests run faster.

The cached response looks something like (condensed for brevity):

```yaml
http_interactions:
- request:
    method: get
    uri: https://eu.httpbin.org/get
    body:
      encoding: ''
      string: ''
    headers:
      User-Agent: libcurl/7.54.0 r-curl/3.2 crul/0.5.2
  response:
    status:
      status_code: '200'
      message: OK
      explanation: Request fulfilled, document follows
    headers:
      status: HTTP/1.1 200 OK
      connection: keep-alive
    body:
      encoding: UTF-8
      string: "{\n  \"args\": {}, \n  \"headers\": {\n    \"Accept\": \"application/json,
        text/xml, application/xml, */*\", \n    \"Accept-Encoding\": \"gzip, deflate\",
        \n    \"Connection\": \"close\", \n    \"Host\": \"httpbin.org\", \n    \"User-Agent\":
        \"libcurl/7.54.0 r-curl/3.2 crul/0.5.2\"\n  }, \n  \"origin\": \"136.152.208.176\",
        \n  \"url\": \"https://httpbin.org/get\"\n}\n"
  recorded_at: 2018-04-03 22:55:02 GMT
  recorded_with: vcr/0.0.7.9324
```

All components of both the request and response are preserved, so that the HTTP 
client (in this case `crul`) can reconstruct its own response just as it would 
if it wasn't using `vcr`.
